---
title: "STATS 506 HW 3"
author: "Anuraag Ramesh"
date: "November 30, 2022"
output:
  pdf_document:
    toc: yes
    df_print: paged
  html_document:
    toc: yes
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo =TRUE, comment=NA, out_width=100, warning = FALSE)
library(data.table)
library(dplyr)
library(tidycensus)
library(tidyverse)
library(RMySQL)
library(stringr)
library(car)
```

## Q1. 

### 1. 

Configuration for Git is set on three levels System, Global and Local.
The system that I am using is a Mac.  
 - The global git configuration file is in my Users folder on the Macintosh HD  
 - The local git configuration file is in the .git folder in the folder hw3 with .R and .Rmd file. 
 
```{r}
writeLines(readLines("/Users/anuraagramesh/.gitconfig", 10))
```

```{r}
writeLines(readLines(".gitignore", 10))
```

### 2. 

```{r}
df_func <- function(n1, n2){
  headers = read.table('Data/2020_Business_Academic_QCQ.txt', sep = ',', nrows = 1,
                       encoding = 'UTF-8')
  df = read.table('Data/2020_Business_Academic_QCQ.txt', sep = ',', skip = n1, 
                  nrows = n2 - n1, fileEncoding="latin1")
  colnames(df) = headers
  df = df %>% select('State', 'County Code', 
                'Employee Size (5) - Location', 
                'Sales Volume (9) - Location', 
                'Census Tract')
  colnames(df) = gsub('-', '', colnames(df))
  colnames(df) = gsub('\\(\\d\\)', '', colnames(df))
  colnames(df) = gsub(' ', '', colnames(df))
  colnames(df) = tolower(colnames(df))
  df <- df[complete.cases(df), ]
  
  return(df)
}
```

### 3. 

```{r}
df = data.frame()
for (i in seq(1, 300001, by = 20000)){
  if(i == 1){
    n1 = i
  }
  else{
    n2 = i
    df1 = df_func(n1, n2)
    n1 = n2
    df = rbind(df, df1)
  }
}

print(head(df))
```

```{r}
agg = df %>% group_by(countycode, censustract) %>%
  summarise(employeesize = sum(employeesizelocation),
            salesvolume = sum(salesvolumelocation))
df1 = data.frame(agg)

df1$censustract = as.character(df1$censustract)

print(head(df1))
```


### 4. 

Table creation in SQL:

CREATE TABLE df1 (
  countycode VARCHAR(255),
	censustract VARCHAR(255),
	employeesize INT,
	salesvolume INT
)

```{r}
host_name = 'localhost'
port_no = 3306
db_name = 'Hw3db'
u_id = 'root'

pwd = Sys.getenv('sqlpwd')

conn = RMySQL::dbConnect(RMySQL::MySQL(), host = host_name, port = port_no, user = u_id,
                         password = pwd, dbname = db_name)

RMySQL::dbWriteTable(conn, name = 'df1', df1, overwrite = TRUE, row.names = FALSE)
```

### 5. 

```{r}
res = dbGetQuery(conn, 'SELECT countycode, censustract, salesvolume FROM df1 ORDER 
                 BY salesvolume DESC LIMIT 10')
print(res)
```

### 6. 

git commit -m "Question 5 Completed"
git push origin main

git branch new  
git checkout new

### 7. 

```{r}
df2 = read.csv('Data/AL.csv')
df2 = df2[c('FIELD19', 'FIELD20', 'FIELD22', 'FIELD45', 'FIELD64', 'FIELD65')]

colnames(df2) = c('householdwealth', 'income', 'home_value', 'state', 'countycode', 'censustract')
df2 = df2[df2$home_value != 0, ]
df2 = df2 %>% group_by(countycode, censustract) %>%
  summarise(wealth = mean(householdwealth),
            income = mean(income),
            homevalue = mean(home_value))
df2$censustract = as.character(df2$censustract)

print(head(df2))
```

### 8. 

CREATE TABLE df2 (
  countycode VARCHAR(255),
	censustract VARCHAR(255),
	wealth FLOAT,
	income FLOAT,
	homevalue FLOAT
)

```{r}
RMySQL::dbWriteTable(conn, name = 'df2', df2, overwrite = TRUE, row.names = FALSE)
```

### 9. 

Git Log:  

commit d398fbb8fa29c92fc9e878a62b0932129cd3c963 (HEAD -> new, origin/new)
Author: Anuraag Ramesh <anuraagr@umich.edu>
Date:   Fri Nov 25 22:55:19 2022 -0500

    Question 8 Completed

commit 210c0f5c9c2219a076f8e70392aa9eb245843c7e (origin/main, main)
Author: Anuraag Ramesh <anuraagr@umich.edu>
Date:   Fri Nov 25 21:51:26 2022 -0500

    Q5 Completed

commit e9353aadc7e50f2f6c1bf456fce013fd6f9321b4 (origin/master)
Author: Anuraag Ramesh <anuraagr@umich.edu>
Date:   Fri Nov 25 19:23:03 2022 -0500

    Q5 Completed
    
HEAD means the current branch that is being checked out and points out the last commit.  

### 10. 

```{r}
Sys.getenv("CENSUS_API_KEY")
census <- get_decennial(geography = 'tract', variables = c('H006001', 'H006002', 
                                                           'H006003', 'H006004','H006005',
                                                           'H006006'), 
                        year = 2010, state = '01')
census = census %>% spread(variable, value)

census$whitepercent = census$H006002/census$H006001
census$blackpercent = census$H006003/census$H006001
census
census$countycode = as.numeric(substr(census$GEOID, 3, 5))
census$countycode = as.character(census$countycode)

census$tract = substr(census$GEOID, 6, 11)
census$tract = as.numeric(census$tract)
census$tract = as.character(census$tract)

head(census)

RMySQL::dbWriteTable(conn, name = 'census', census, overwrite = TRUE, row.names = FALSE)
```

### 11. 

```{r}
combine = dbGetQuery(conn, 'SELECT d2.censustract, d2.wealth, d2.income, 
d2.homevalue, d1.employeesize, d1.salesvolume, 
c.whitepercent, c.blackpercent FROM 
df2 d2 JOIN df1 d1 ON d2.countycode = d1.countycode AND
d2.censustract = d1.censustract 
JOIN census c ON c.countycode = d1.countycode AND 
c.tract = d1.censustract')
head(combine)
```
Two variables that I would like to control the effects of are **average home size(sq. ft)** and **quality of construction rating**. Both these factors might affect average home valuations in a tract.  

### 12. 

Commands to do the following:

git commit -m "Question 11 Completed"  
git log  
git checkout main  
git merge new  

Git Log:  

commit a5226df2424f4f91b254264b54fa1ca938c77a17 (HEAD -> new)
Author: Anuraag Ramesh <anuraagr@umich.edu>
Date:   Sat Nov 26 23:49:33 2022 -0500

    Question 11 Completed

commit d398fbb8fa29c92fc9e878a62b0932129cd3c963 (origin/new)
Author: Anuraag Ramesh <anuraagr@umich.edu>
Date:   Fri Nov 25 22:55:19 2022 -0500

    Question 8 Completed

commit 210c0f5c9c2219a076f8e70392aa9eb245843c7e (origin/main, main)
Author: Anuraag Ramesh <anuraagr@umich.edu>
Date:   Fri Nov 25 21:51:26 2022 -0500

    Q5 Completed

commit e9353aadc7e50f2f6c1bf456fce013fd6f9321b4 (origin/master)
Author: Anuraag Ramesh <anuraagr@umich.edu>
Date:   Fri Nov 25 19:23:03 2022 -0500

    Q5 Completed
    

The way to reset back to the old repository is to use: `git reset --hard HEAD^`  


### 13. 

```{r}
#Correlation matrix
cor(combine[c('wealth', 'income', 'homevalue', 'employeesize', 
              'salesvolume', 'blackpercent', 'whitepercent')], use = 'complete.obs')

#Model only having the percentage of white people in a tract
model_1 = lm(homevalue ~ whitepercent, data = combine)
summary(model_1)

#Model only having the percentage of black people in a tract
model_2 = lm(homevalue ~ blackpercent, data = combine)
summary(model_2)

#First model
model_3 = lm(homevalue ~ wealth + employeesize + salesvolume + blackpercent, 
             data = combine)
summary(model_3)

#Variance Inlation Factors
vif(model_3)

#Standardizing the data
combine_standardized <- 
  combine %>% 
  mutate(wealth_s = scale(wealth),
         income_s = scale(income), 
         employeesize_s = scale(employeesize),
         salesvolume_s = scale(salesvolume),
         whitepercent_s = scale(whitepercent),
         blackpercent_s = scale(blackpercent),
         homevalue_s = scale(homevalue))

model_4 = lm(homevalue ~ wealth_s + employeesize_s + salesvolume_s + 
               blackpercent_s, data = combine_standardized)
summary(model_4)
```

From the correlation matrix as well as single variable models(model_1 and model_2), we can clearly see that the percentage of white people in a tract is positively correlated with home valuation. On the other hand, the percentage of black people in tract is negatively correlated with home valuation.   

We can see that income and wealth is highly correlated so we remove one of them while creating a model(model_3). We calculate the variance inflation factor(VIF) to check if the co-variates are highly correlated.  

**In the final model, we can see that whitepercent/blackpercent is significant in predicting home valuation.** This helps us answer thw initial question if racial bias is inherent in home valuattion.  
One confounding factor is that the blackpercent co-variate has a positive coefficient. This is conflicting with the correlation matrix and single variable models, which suggest a negative realtion. This can be justified by the fact that the coefficients for multi-variable regression cannot be taken at face value. The fact that blackpercent and wealth are correlated plays an essential part in changing the coefficients, a high blackpercent could lead to a lower average wealth in a tract.  



## Q2.

### 1. 

A core is a computational unit that actually runs the code that we want on the HPC cluster. It can actually consist of multiple processors.  

A node is the server/computer where the memory as well as the processors are installed.  

A compute node is where the computation happens. The user specifies the job/application to be run on the compute node using a fixed set of resources. The compute node consists of processors, memory and GPU.

A login node is a place for users to interact with a cluster. Users can use a login node to view files, results as well as submit jobs.

### 2. 

For an interactive session we use salloc instead of submitting a batch job.

`salloc --nodes=1 --mem-per-cpu=32GB --cpus-per-task=4 --time=03:00:00`

### 3. 

Path to my scratch directory: `/scratch/stats506s001f22_class_root/stats506s001f22_class/anuraagr`  


Creating a symbolic link from my scratch to home directory:

`ln -s /scratch/stats506s001f22_class_root/stats506s001f22_class/anuraagr`  


Deleting a symbolic link does not affect the original directory, as it is a soft link.




